% Resume template

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
%\addtolength{\oddsidemargin}{-.6in}
%\addtolength{\evensidemargin}{-.4in}
%\addtolength{\textwidth}{1.15in}
%\addtolength{\topmargin}{-.7in}
%\addtolength{\textheight}{1.4in}

% Adjust margins
\setlength{\oddsidemargin}{-0.5in}    
\setlength{\evensidemargin}{-0.5in}   
\setlength{\textwidth}{7.5in}      
\setlength{\topmargin}{-0.6in}         
\setlength{\textheight}{10in}        

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

\newcommand{\resumeItem}[1]{
  \item \small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\highlightItem}[1]{
  \item \textendash\ \small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\projectSubheading}[2]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{}
\renewcommand\labelitemii{}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    {\large \scshape Eli D. Case} \\ \vspace{1pt}
    \small \raisebox{-0.1\height}\faPhone\ 865-809-3561 ~ \href{mailto:elicase4@gmail.com}{\raisebox{-0.2\height}\faEnvelope\  \underline{elicase4@gmail.com}} ~ 
    \href{https://linkedin.com/in/elicase4}{\raisebox{-0.2\height}\faLinkedin\ \underline{linkedin.com/in/elicase4}}  ~
    \href{https://github.com/elicase4}{\raisebox{-0.2\height}\faGithub\ \underline{github.com/elicase4}}
\end{center}

%-----------SEEKING-STATEMENT-----------
\begin{center}
  \vspace{4pt}
  \textit{\textbf{Seeking an entry-level position in Mechanical Engineering or Software Engineering.}}
  \vspace{-2pt}
\end{center}

%-----------EDUCATION-----------
\section{EDUCATION}

  \resumeSubHeadingListStart
    
    \resumeSubheading
      {Rice University}{May 2024 -- August 2025}
      {M.S. Mechanical Engineering}{Houston, TX}
      \resumeItem{GPA: 4.00/4.00}
    \resumeSubheading
      {Rice University}{August 2020 -- May 2024}
      {B.S. Mechanical Engineering, Minor Computational and Applied Mathematics}{Houston, TX}
      \resumeItem{GPA 3.98/4.00, summa cum laude}

  \resumeSubHeadingListEnd
\vspace{-16pt}

%-----------SELECTED CAREER HIGHLIGHTS-----------
\section{SELECTED HIGHLIGHTS}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \highlightItem{As a first-year undergraduate, implemented Computational Fluid Dynamics (CFD) and Finite Element Analysis (FEA) procedures for a student rocketry team's hybrid rocket propulsion system, leading to the adoption of high-fidelity simulations across multiple design teams within the organization.}

    \highlightItem{Designed and implemented a nozzle, resistive heater, and control system software for a cold spray additive manufacturing device prototype on a \$5,000 budget over 8 months. This senior capstone project won three awards for invention, innovation, and presentation at an annual design showcase.}

    \highlightItem{Conducted background research, performed product testing, and gathered evidence to draft an expert witness report for a class-action lawsuit that resulted in a \$20,000,000 favorable settlement.} 
    
\end{itemize}
\vspace{-16pt}

%-----------EXPERIENCE-----------
\section{EXPERIENCE}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Team for Advanced Flow Simulation and Modeling}{January 2022 -- Present}
      {Research Assistant (Tayfun Tezduyar PhD, Kenji Takizawa PhD)}{Houston, TX}
      \resumeItemListStart
        \resumeItem{A research group with members at Rice University and Waseda University focusing on computational engineering analysis with advanced flow simulation and modeling methods developed in-house. The role has consisted of projects implementing mesh refinement techniques and multiphase flow modeling with phase-field approaches. Other minor responsibilities include training new members, maintaining the lab server network, and task automation via scripting.}
      \resumeItemListEnd   
    \vspace{-12pt}
    \resumeSubheading
      {UI Expert -- Expert Witness Group Co.}{May 2021 -- September 2021}
      {Intern}{Seattle, WA}
      \resumeItemListStart
        \resumeItem{Assisted an Expert Witness with a specialization in UI/UX design. Responsibilities included conducting background research for cases, analyzing classified documents, and drafting expert witness reports and presentations.}
      \resumeItemListEnd   
 
    \resumeSubHeadingListEnd
 \vspace{-16pt}

 %---------PROJECTS---------
\section{CAPSTONE PROJECT}

    \resumeSubHeadingListStart
      \projectSubheading
        {Aeroforge3D -- Cold Spray Additive Manufacturing Device}{August 2023 -- Present}
        \resumeItemListStart
          \resumeItem{An interdisciplinary, student-lead engineering capstone project at Rice University. Designed several subsystems, aided in prototyping and manufacturing, and presented at an annual capstone project fair. The project has been renewed as an ongoing capstone project with original members acting as project advisors.}
        \resumeItemListEnd   
  \resumeSubHeadingListEnd
\vspace{-16pt}

%-----------EXTRACURRICULARS---------------
\section{EXTRACURRICULARS}
    
    \resumeSubHeadingListStart
        
        \resumeSubheading{Rice Eclipse}{August 2020 -- May 2022}{Fluid Flow Analysis Team Lead}{Rice University}
          \resumeItemListStart
             \resumeItem{Rice's largest student-run engineering organization focused on designing competition rockets. Lead a subteam in the design of rocket propulsion system components through experimentation, engineering analysis tools (systems modeling, Computational Fluid Dynamics, Finite Element Analysis), and machining (lathing and milling).}
          \resumeItemListEnd   
        
    \resumeSubHeadingListEnd
\vspace{-16pt}

%-----------AWARDS-----------
\section{AWARDS}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Academic} \\
     {-- 2024 Alan J. Chapman Award} \\
     {-- 2024 Thomas Michael Panos Family Superior Engineering Student Award} \\
     \vspace{2pt}
     \textbf{Project (Cold Spray Additive Manufacturing Device)} \\
     {-- Herschel M. Rich Invention Award} \\
     {-- Willy Revolution Outstanding Innovation Award -- First Place}\\ 
     {-- Excellence in Capstone Engineering Award} \\
    }}
 \end{itemize}
 \vspace{-16pt}

%-----------SKILLS-----------
\section{SKILLS}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Programming Tools}{: Python (Numpy, Scipy, Matplotlib, NetworkX), C++ (OMPL, Boost, OpenMP, OpenMPI, Arduino), C, Cuda, Bash, Git, MATLAB, Julia} \\
     \textbf{Engineering Design Tools}{: Microsoft Excel, Solidworks, Fusion 360, Ansys, COMSOL, Simulink, Pointwise} \\
    }}
 \end{itemize}
 \vspace{-16pt}

%-----------KEYWORDS-----------
\section{KEYWORDS}
   \footnotesize{computational fluid mechanics finite element analysis aerospace rocket propulsion cold spray additive manufacturing nozzle design method of characteristics injector plate science fluid structure interaction multiphase flow expert witness report mesh generation mesh refinement embedded software programming applied mathematics heat transfer compressible flow high perforamnce computing programming scripting}

\vfill

Eli Case, Resum\'e, Page 2 \hfill \small \raisebox{-0.1\height}\faPhone\ 865-809-3561 ~ \hfill \href{mailto:elicase4@gmail.com}{\raisebox{-0.2\height}\faEnvelope\  \underline{elicase4@gmail.com}} ~ 

\end{document}
