% Resume template

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\centering\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

\begin{document}

\begin{center}
    {\large \scshape Eli D. Case} \\ \vspace{1pt}
    \small \raisebox{-0.1\height}\faPhone\ 865-809-3561 ~ \href{mailto:elicase4@gmail.com}{\raisebox{-0.2\height}\faEnvelope\  \underline{elicase4@gmail.com}} ~ 
    \href{https://linkedin.com/in/elicase4}{\raisebox{-0.2\height}\faLinkedin\ \underline{linkedin.com/in/elicase4}}  ~
    \href{https://github.com/elicase4}{\raisebox{-0.2\height}\faGithub\ \underline{github.com/elicase4}}
    \vspace{-4pt}
\end{center}

%-----------SELECTED CAREER HIGHLIGHTS-----------
\section{Complete Accomplishments Inventory}
  \vspace{2pt} 
  \begin{enumerate} %[leftmargin=0.15in, label={}]
    
    \item Graduated summa cum laude with a GPA of 3.98, receiving two awards for academic excellence during my final year of undergraduate studies.
    
    \item As a first-year undergraduate, implemented Computational Fluid Dynamics (CFD) and Finite Element Analysis (FEA) procedures for a student rocketry team’s hybrid rocket propulsion system, leading to the adoption of high-fidelity simulations across multiple design teams within the organization.
    
    \item Assisted in manufacturing injector plates and bell nozzles for a hybrid rocket propulsion system, which was successfully launched at a university competition. This marked the first student-launched hybrid rocket in Texas to reach the 30,000 ft altitude category.

    \item As an upperclassman, mentored members of a student rocketry team performing engineering simulations in the areas of structural analysis, fluid-structure interaction, and compressible flow problems.

    \item Designed and implemented a nozzle, resistive heater, and control system software for a cold spray additive manufacturing device prototype on a \$5,000 budget over 8 months. The project won three awards for invention, innovation, and presentation at an annual design showcase.

    \item Conducted background research, performed product testing, and gathered evidence to draft of an expert witness report (report was not substantially changed) for a class-action lawsuit that resulted in a \$20,000,000 settlement.

    \item Served as an academic fellow for 3 years as an undergraduate, tutoring other undergraduates students in introductory math, physics, and applied mathematics courses.  

    \item Developed custom software in Python for T-Spline mesh refinement for specialized mesh data structures. 

    \item Created software in Python to automate the process of rendering images involving multiple computational geometries for use in journal publications. The process of depth sorting multiple computational geometries in a single image previously required a manual time consuming process. 

    \item As an upperclassman in high school, worked a part-time job in at a pizzeria 12-20 hours a week while maintaining a 4.00 GPA. Advanced from a dishwasher to the kitchen line rotation within a few months, and helped cover shifts to ensure a smoothly operating dinner service.   

  \end{enumerate}

\end{document}
