% Resume template

\documentclass[letterpaper,11pt]{letter}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\newcommand{\paragraphbreak}{\vspace{5pt}}

% Adjust margins
\setlength{\oddsidemargin}{-0.25in}
\setlength{\evensidemargin}{-0.25in}
\setlength{\textwidth}{7.0in}
\setlength{\topmargin}{-0.6in}
\setlength{\textheight}{10in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\centering\large\bfseries
}{}{0em}{}[\color{black} \titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

\begin{document}

\begin{center}
    {\large \scshape Eli D. Case} \\ \vspace{1pt}
    \small \raisebox{-0.1\height}\faPhone\ 865-809-3561 ~ \href{mailto:elicase4@gmail.com}{\raisebox{-0.2\height}\faEnvelope\  \underline{elicase4@gmail.com}} ~ 
    \href{https://linkedin.com/in/elicase4}{\raisebox{-0.2\height}\faLinkedin\ \underline{linkedin.com/in/elicase4}}  ~
    \href{https://github.com/elicase4}{\raisebox{-0.2\height}\faGithub\ \underline{github.com/elicase4}}
    \vspace{-4pt}
\end{center}

\section{}

\today \\

\paragraphbreak

Dear Hiring Manager,

\paragraphbreak

I am excited to apply for the Water Technology Engineering position at Oxy. With several years of experience using computational technologies, experimentation, and data analysis across various projects, I bring strong problem-solving skills and team-project experience that would be valuable to the Water Technology and Strategy Team at Oxy. 

\paragraphbreak

% Oxy specific paragraph about how you will thrive in the role
I admire Oxy's mission to solve environmental challenges through pushing the boundaries of industry standards and expectations through the development of innovative energy and petrochemical products. As someone starting their career, I am hoping to learn, grow, and contribute in a role requiring strong problem-solving skills, as well as interfacing with various project stakeholders. 

\paragraphbreak

% Talk about general prior experience and specific accomplishments in prior roles

As shown on my resume, my prior experience working on team-based engineering projects and academic research teams have often required in-depth exploration into specialized scientific topics to meet project deliverables. I previously worked on a hybrid rocket propulsion system project for a student engineering team and a cold spray additive manufacturing project for my senior capstone project. In these projects, I used Computational Fluid Dynamics (CFD) and Finite Element Analysis (FEA) for design optimization, performed on-site testing and prototyping, and collected data for analysis of test results. In academic research, I have worked in-depth with various aspects of computational technologies, including mesh generation, solver development, and applications of physics-based modeling to large-scale engineering problems. In these roles, I have become accustomed to tackling technically challenging problems, working in engineering teams, and interfacing with project stakeholders.  

\paragraphbreak

% Closing paragraph about attached resume and information and how you look forward to contributing to the company

My resume is attached to this application showcasing specific aspects of my prior roles and the skills each projects required. Please don't hesitate to ask for any additional information or documentation related to these prior projects. Thank you for your time and consideration, and I look forward to further sharing how I can contribute to the success of the Water Technology and Strategy Team at Oxy.

\paragraphbreak

Sincerely, \\
Eli Case

\end{document}
