% Resume template

\documentclass[letterpaper,11pt]{letter}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\newcommand{\paragraphbreak}{\vspace{5pt}}

% Adjust margins
\setlength{\oddsidemargin}{-0.25in}
\setlength{\evensidemargin}{-0.25in}
\setlength{\textwidth}{7.0in}
\setlength{\topmargin}{-0.6in}
\setlength{\textheight}{10in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\centering\large\bfseries
}{}{0em}{}[\color{black} \titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

\begin{document}

\begin{center}
    {\large \scshape Eli D. Case} \\ \vspace{1pt}
    \small \raisebox{-0.1\height}\faPhone\ 865-809-3561 ~ \href{mailto:elicase4@gmail.com}{\raisebox{-0.2\height}\faEnvelope\  \underline{elicase4@gmail.com}} ~ 
    \href{https://linkedin.com/in/elicase4}{\raisebox{-0.2\height}\faLinkedin\ \underline{linkedin.com/in/elicase4}}  ~
    \href{https://github.com/elicase4}{\raisebox{-0.2\height}\faGithub\ \underline{github.com/elicase4}}
    \vspace{-4pt}
\end{center}

\section{}

\today \\

\paragraphbreak

Dear Hiring Manager,

\paragraphbreak

I am excited to apply for the CFD Consultant position at WSP. With extensive experience in Computational Fluid Dynamics (CFD) across various projects, I bring strong problem-solving skills and a passion for computational approaches in design that would be valuable to the Built Ecology team. WSP's reach across a broad set of engineering projects ranging from infrastructure design to operations enhancement in consulting make WSP an ideal place to begin my career.

\paragraphbreak

During my time with Rice Eclipse as the Fluid Flow Analysis Team Lead, I led efforts to integrate CFD and Finite Element Analysis (FEA) workflows into existing design processes for a rocket propulsion sub-team. I initiated this effort by solving problems in the areas heat transfer, fluid flow, and coupled multiphysics analysis. With the success of these computational approaches, I mentored team members across the organization in fluid flow, heat transfer, and structural analysis to make the use of advanced computational tools more common. Additionally, the propulsion system I helped design, manufacture, and test was launched in the 30,000 ft category at Spaceport America Cup, making it the first hybrid rocket from Texas to successfully launch in that altitude category.

\paragraphbreak

For my engineering capstone project, I worked on a student initiative to design and build a cold spray additive manufacturing device on a \$5,000 budget. This project was an ambitious undertaking, as cold spray additive manufacturing is a novel technology and we were operating with a tightly constrained budget. Among other roles, I used CFD to successfully design a printer nozzle and resistive heater system that were fundamental for the device's operation. The final prototype device won three awards for innovation, invention, and presentation at an annual design showcase.

\paragraphbreak

Currently, as a graduate student at Rice University, I am researching phase field modeling approaches for multiphase flow. This research project involves programming new features for an existing fluid solver codebase, validating the new solver with test problems, and solving industrial-level problems in multiphase flows. In working on this research project, I have deepened my understanding of CFD, both from a programming and application perspective.

\paragraphbreak

As someone who has worked on technically challenging projects as a student, I desire to continue to be part of a project team solving complex engineering and design challenges. I am always eager to learn new skills and take on new challenges to get the job done, and I believe I would thrive in WSP's environment as a result.

\paragraphbreak

Thank you for your time and consideration, and I look forward to discussing the position further.

\paragraphbreak

Sincerely, \\
Eli Case

\end{document}
